FinalManuscript_DISCS_UG

### 2018-10-07 parts/01_introduction_03objectives.tex
Updated Chapter 1
updated chapter 1 to have references to facial recognition

A paper published in 2009 by Ziad, et. al. presents \textit{CryptoImg}, a library for the  Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}. While \textit{CryptoImg} demonstrates that various image manipulation operations are possible in a homomorphic cryptosystem, we believe this study can be extended by considering other known homomorphic encryption schemes, such as those found in~\cite{li_elliptic_2012, hutchison_fully_2010}. Our study aims to provide an objective comparison of various homomorphic cryptosystems currently in the literature, as they would be used in encrypted image manipulation.

Our main research objective is to assess the practicality of various homomorphic cryptosystems in image encryption. Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}. Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed~\cite{li_elliptic_2012}. Finally, as data security is the primary purpose of cryptosystems, we want to evaluate the security of homomorphic cryptosystems as image encryption schemes.

In summary, in this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homomorphic encryption schemes to common image processing operations, in other words, determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
    \item Compare the time efficiency of common image processing operations under known homomorphic encryption schemes;
    \item Create a library for OpenCV to allow for convenient use and comparison of these homomorphic encryption schemes.
\end{enumerate}

>>>>

Previous attempts in the literature to provide image processing tasks such as image manipulation \cite{ziad_cryptoimg:_2016} and  facial recognition \cite{hutchison_privacy-preserving_2009} have primarily used the Paillier and DGK cryptosystems to perform linear operations on encrypted data. In this study, we extend this research to provide an objective comparison of various homomorphic cryptosystems currently in the literature in performing non-linear operations, as opposed to just linear operations, and facial detection, as opposed to just facial recognition.

Our main research objective is to assess the practicality of various homomorphic cryptosystems in image encryption. Homomorphic cryptosystems are known to be slower in terms of encryption, operation, and decryption time~\cite{sen_homomorphic_2013}. Furthermore, the operations on encrypted data supported by homomorphic cryptosystems are limited, and some schemes require preprocessing to be performed on images, limiting the range of operations which can be performed efficiently~\cite{li_elliptic_2012}.

In summary, in this study, we wish to
\begin{enumerate}
    \item Compare the applicability of known homomorphic encryption schemes to common image processing operations, in other words, determine which schemes admit more image processing operations and extend known cryptosystems to support more operations, if possible;
    \item Compare the time efficiency of common image processing operations under known homomorphic encryption schemes;
    \item Create a library for the Open Source Computer Vision Library (OpenCV) to allow for convenient use and comparison of these homomorphic encryption schemes for image processing and facial recognition.
\end{enumerate}

### 2018-10-07 parts/01_introduction_04significanceofstudy.tex
Updated Chapter 1
updated chapter 1 to have references to facial recognition

This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}. The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, support for more complicated image processing operations such as image convolution must be demonstrated as well. While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets algorithms for which statistical tests have not been performed for image processing operations.

>>>>

This study aims to directly address one of the current problems in the research of homomorphic cryptosystems: the practicality of homomorphic encryption~\cite{sen_homomorphic_2013}. The literature shows existing homomorphic cryptosystems and how they support primitive operations (usually addition and multiplication) on encrypted data, however, for homomorphic cryptosystems to be useful for practical use, efficient support for more complicated image processing operation must be demonstrated as well. While implementations of image processing operations in a homomorphic cryptosystem exist in the literature~\cite{ziad_cryptoimg:_2016, garay_algorithms_2014}, our study targets the more computationally intensive task of facial detection.

### 2018-10-07 parts/01_introduction_05scopeandlimitations.tex
Updated Chapter 1
updated chapter 1 to have references to facial recognition

We will implement and test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
	\item The Benlano cryptosystem~\cite{benaloh_dense_1994} which is a probabilistic cryptosystem which relies on the hardness of the discrete logarithm.
	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
	\item A fully homomorphic encryption scheme by Smart and Vercauteren \cite{hutchison_fully_2010}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Image adjustment
	\item Spatial filters/morphological operations
\end{enumerate}
We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	%\item Tests for preservation of image quality after encryption and decryption
	%\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	%\end{enumerate}
	%\item Tests for cryptographic security
	%\begin{enumerate}
	%	\item Information entropy analysis
	%	\item Correlation coefficient analysis
	%	\item Differential analysis
  %      \begin{enumerate}
  %          \item Number of Pixel Change Rate (NPCR)
  %          \item Universal Average Change Intensity (UACI)
  %      \end{enumerate}
	%\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology.
Both grayscale and color images will be used in the study.

The study will only consider the operation of the stated algorithms in a single computer. Client-server models for secure data storage and operation will not be considered.

>>>>

We will implement and test the following algorithms:
\begin{enumerate}
	\item A variant of the Paillier cryptosystem~\cite{stern_public-key_1999} which supports floating-point operations, used in \textit{CryptoImg}~\cite{ziad_cryptoimg:_2016}.
	\item The Damgård-Geisler-Krøigaard (DGK) cryptosystem~\cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is primarily used for secure integer comparison.
	\item A fully homomorphic encryption scheme by Dasgupta and Pal, which uses polynomial rings~\cite{dasgupta_design_2016}.
	\item The Brakerski-Gentry-Vaikuntanathan (BGV) cryptosystem \cite{cryptoeprint:2011:277}, an improvement on the lattice-based cryptosystem by Gentry~\cite{gentry_fully_2009}, with optimizations from Smart, Vercauteren and Halevi \cite{hutchison_fully_2010, cryptoeprint:2011:566}.
\end{enumerate}
We will implement and test the following categories of image manipulation operations:
\begin{enumerate}
	\item Non-linear image intensity adjustment (logarithm and power-log transformations)
	\item Facial detection and recognition using the eigenface approach \cite{turk_eigenfaces_1991}.
\end{enumerate}
We will adopt the benchmark for evaluating image quality of image encryption schemes presented by Ahmed, et. al~\cite{ahmed_benchmark_2016}. The presented benchmark reflects many tests used in other literature~\cite{ahmad_efficiency_2012, wu_npcr_2011}.
\begin{enumerate}
	%\item Tests for preservation of image quality after encryption and decryption
	%\begin{enumerate}
		\item Mean Squared Error (MSE)
		\item Peak Signal to Noise Ratio (PSNR)
		\item Structural Similarity Index (SSIM)
	%\end{enumerate}
	%\item Tests for cryptographic security
	%\begin{enumerate}
	%	\item Information entropy analysis
	%	\item Correlation coefficient analysis
	%	\item Differential analysis
  %      \begin{enumerate}
  %          \item Number of Pixel Change Rate (NPCR)
  %          \item Universal Average Change Intensity (UACI)
  %      \end{enumerate}
	%\end{enumerate}
\end{enumerate}
A detailed overview of the above will be provided in the methodology. Grayscale images will be used in the study.
A client-server model for secure computation will be assumed to allow operations such as secure comparison and exponentiation.

### 2018-10-07 parts/02_relatedliterature_01cryptoimg.tex
Updated Chapter 1
updated chapter 1 to have references to facial recognition

\section{CryptoImg}
A recent attempt in the literature to implement privacy-preserving image processing is the \textit{CryptoImg} software library, presented by Ziad, et al. in 2016 \cite{ziad_cryptoimg:_2016}. The CryptoImg library assumed a client-server model wherein a client requests image processing operations from a server. A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents. Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
\begin{figure*}[!ht]
    \centering
    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/ClientServerModel.png}
    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
    \label{fig:clientserver}
\end{figure*}
The CryptoImg library implemented the following:
\begin{enumerate}
	\item Extending the Paillier homomorphic cryptosystem which operate on integer plaintexts so that they can operate on real number plaintexts;
	\item Developing protocols for and implementing the following image processing operations
	\begin{enumerate}
		\item Image negation and brightness adjustment
		\item Spatial filters (for noise reduction, edge detection and sharpening)
		\item Morphological operations
		\item Histogram equalization
	\end{enumerate}
\end{enumerate}
For image negation and spatial filters, the protocols specified by CryptoImg allow all image processing operations to be performed on the server. However, due to limitations in the Pallier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.

>>>>

\section{CryptoImg}
A paper published in 2009 by Ziad, et. al. attempts to implement privacy-preserving image processing using \textit{CryptoImg}, a library for the Open Source Computer Vision Library (OpenCV)~\cite{bradski_opencv_2000} which implements various homomorphic encryption and image processing routines using the Paillier homomorphic cryptosystem~\cite{ziad_cryptoimg:_2016}. The CryptoImg library assumed a client-server model wherein a client requests image processing operations from a server. A client first encrypts a digital image and sends the image securely to a server, which then operates on the encrypted image without revealing its contents. Then the resulting image is sent back to the client, which decrypts the image to recover the desired output.
\begin{figure*}[!ht]
    \centering
    \includegraphics[width=\textwidth,\keepaspectratio]{Figures/ClientServerModel.png}
    \caption{Client-server architecture used by \textit{CryptoImg} \cite{ziad_cryptoimg:_2016}}
    \label{fig:clientserver}
\end{figure*}
The CryptoImg library implemented the following:
\begin{enumerate}
	\item Extending the Paillier homomorphic cryptosystem which operate on integer plaintexts so that they can operate on real number plaintexts;
	\item Developing protocols for and implementing the following image processing operations
	\begin{enumerate}
		\item Image negation and brightness adjustment
		\item Spatial filters (for noise reduction, edge detection and sharpening)
		\item Morphological operations
		\item Histogram equalization
	\end{enumerate}
\end{enumerate}
For image negation and spatial filters, the protocols specified by CryptoImg allow all image processing operations to be performed on the server. However, due to limitations in the Pallier cryptosystem, the protocols presented for morphological operations and histogram equalization require both the client and the server to perform image processing calculations, although the server performs a significant portion of the processing.

### 2018-10-07 parts/02_relatedliterature_05partiallyhomomorphic.tex
Updated Chapter 1
updated chapter 1 to have references to facial recognition

\subsection{The DGK Cryptosystem}
The DGK cryptosystem was published by Damgard, Geisler, and Krøigaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.

>>>>

\subsection{The DGK Cryptosystem}
The DGK cryptosystem was published by Damgård, Geisler, and Krøigaard in 2007 in an effort to create a secure integer comparison scheme \cite{pieprzyk_efficient_2007, cryptoeprint:2008:321} which is widely used in the literature \cite{veugen_improving_2012}.
